### 2015-05-07 SAPSE2015/camera-ready/computingDerivSLA.tex
New Directory: SAPSE2015 contains the camera-ready version (final)

%A query has associated preferences  expressed as macroscopic constraints (i.e. user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy-preserving constraints, partial/full results, delivery mode. These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).

%As said before, we assume that services export their \textit{agreed SLAs} that define measures that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.  A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}). The service SLA measures  that we consider in our example are: cost, availability, freshness, provenance, location, duration of the engagement, privacy-preserving status. Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.

The {\em derived SLA} is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures that can come from the evaluation of measures expressed in the cloud subscription of the user. 
The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.

In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said in previous section, will guide the evaluation of the query. 
These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract. For example: 
\begin{trivlist}\sf\footnotesize
 \item[~-~ total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1;
 \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$};
 ~-~freshness: non;
 \item[~-~provenance:] all services involved must be $expert$;
  ~-~duration: 7 days;
 \item[~-~I/0 volume/month:] 8GB;
  ~-~reputation level: $\geq$ threshold;
 \item[~-~storageSpace:] 1GB.
 \end{trivlist}

Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by {\em agreed SLAs} and coarse grained measures used in user preferences statements. 
It specifies also how to compute coarse grained measures with fine grained ones. 
For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The {\em derived SLA} can be seen as a set of inequations that have to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.  
This later step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between {\em agreed SLA}s and the {\em derived SLA}. In order to address this problem we introduce the notion of  {\em integration SLA}. 
%and thus the need for an adaptive setting.
%Negotiation of implied SLAs depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query). This negotiation can be expensive and may not scale well.

>>>>

The {\em derived SLA} is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. These measures can come from the evaluation of simpler measures expressed in the cloud subscription of the user. 
The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.

In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said before, will guide the evaluation of the query. 
These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract. For example: 
\begin{trivlist}\sf\footnotesize
 \item[~-~ total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1;
 \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$};
 ~-~freshness: non;
 \item[~-~provenance:] all services involved must be $expert$;
  ~-~duration: 7 days;
 \item[~-~I/0 volume/month:] 8GB;
  ~-~reputation level: $\geq$ threshold;
 \item[~-~storageSpace:] 1GB.
 \end{trivlist}

Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by {\em agreed SLAs} and coarse grained measures used in user preferences statements. 
It specifies also how to compute coarse grained measures with fine grained ones. 
For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The {\em derived SLA} can be seen as a set of inequations that have to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.  
This latter step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between {\em agreed SLA}s and the {\em derived SLA}. In order to address this problem we introduce the notion of  {\em integration SLA} (defined in  Section \ref{sec:queryProcessOpt}). 
%and thus the need for an adaptive setting.
%Negotiation of implied SLAs depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query). This negotiation can be expensive and may not scale well.

### 2015-05-07 SAPSE2015/old-versions/old-1/useCase.tex
New Directory: SAPSE2015 contains the camera-ready version (final)

\begin{figure*}
\center{
\includegraphics[width=0.65\textwidth]{use-case.png}
\caption{General distributed data storage service.\label{fig:storage}}}
\end{figure*}

According to our example scenario, we conducted an experimental experience for implementing our data integration approach on a multi-cloud environment. We focussed on the implementation of a data as a service layer that integrates content from different services related to education but also related on data producers and consumers. Figure \ref{fig:storage} shows the general architecture of our scenario, deployed on Window Azure data store services and on Jelastic (https://jelastic.com), an open free cloud provider where we installed NE4J and Mongo NoSQL stores. The multi-cloud data as a service layer is a data provision platform storing clean data sets stemming from public data services (Linked in, Tweeter, Facebook) accessible on Internet and also from private ones.

@@

We proposed a global service that gives access to these databases in an integrated way, and can receive queries using a pivot language, UNQL in our case. The global service implements a negotiation process for dealing with SLA and  the  query rewriting process.

>>>>

\begin{figure*}
\center{
\includegraphics[width=0.60\textwidth]{use-case.png}
\caption{General distributed data storage service.\label{fig:storage}}}
\end{figure*}

According to our example scenario, we conducted an experience for implementing our data integration approach on a multi-cloud environment. We focussed on the implementation of a data as a service layer that integrates content from different services related to education but also related on data producers and consumers. Figure \ref{fig:storage} shows the general architecture of our scenario, deployed on Window Azure data store services and on Jelastic (https://jelastic.com), an open free cloud provider where we installed NE4J and Mongo NoSQL stores. The multi-cloud data as a service layer is a data provision platform storing clean data sets stemming from public data services (Linked in, Twitter, Facebook) accessible on Internet and also from private ones.

@@

We proposed a global service that gives access to these databases in an integrated way, and can receive queries using a pivot language, UNQL in our case. The global service implements a  process for dealing with SLA and  the  query rewriting process. Global queries are expressed in UNQL and expected SLA in documents containing constraint expression are un-equalities as shown previously. For the time being our experiment does not deales with SLA derivation for choosing data services. SLA measures concern the delay in which results are delivered, the size of results, and the period in which queries are re-executed in order to get new or fresh data.

### 2015-05-07 SAPSE2015/toSubmit/conclusions.tex
New Directory: SAPSE2015 contains the camera-ready version (final)

Current big data settings impose  to consider SLA and different data delivery models. We believe that given the volume and the complexity of query evaluation that includes steps that imply greedy computations, it is important to combine and revisit well-known solutions  adapted to these contexts. We are  developing  strategies and algorithms overviewed in this paper and applying them to energy consumption applications and to elections and political campaign data integration to guide decision making on campaign strategies.

The diversity of mentioned application domains highlights the difficulty regarding SLA manipulation. Indeed, cloud, service, and user SLAs could be expressed differently in term of clauses, formalism and content. The multi-cloud environment emphasizes this heterogeneity.

The main issue when launching an integration process is to obtain the most accurate answer meeting the best user preferences. One of the possibilities when studying the integration is to accept the integration process in an incremental  manner so that the query will continue to be evaluated till satisfying the set of QoS and non functional constraints expressed by the user. To our knowledge, the incremental production of a solution is beyond  the scope of the current methods for rewriting service compositions and represents a challenge to the area.
Furthermore, the integration SLA generation step is outstanding study. In fact the integration SLA should indicate the negotiation result with the aim to reuse it in further integration.

>>>>

Current big data settings impose  to consider SLA and different data delivery models. We believe that given the volume and the complexity of query evaluation that includes steps that imply greedy computations, it is important to combine and revisit well-known solutions  adapted to these contexts. We are currently developing the strategies and algorithms sketched here applied to energy consumption applications and also to elections and political campaign data integration in order to guide decision making on campaign strategies.

Furthermore, the integration SLA generation step is outstanding study. In fact the integration SLA should indicate the negotiation result with the aim to reuse it in further integration. One of the possibilities when studying the integration is to accept the integration process in an incremental  manner so that the query will continue to be evaluated till satisfying the set of QoS and non functional constraints expressed by the user. To our knowledge, the incremental production of a solution is beyond  the scope of the current methods for rewriting service compositions and represents a challenge to the area.
